### 2015-11-25 _knitr-posts/2015-05-25-stan-ricker-missing-values.Rmd
Quick update to CV

```{r stan-impute1}
set.seed(1)
N <- 50         # number of time steps
x <- 1:N        # time step values
y <- rep(NA, N) # vector to hold (scaled) abundance values
y[1] <- 1       # initial scaled abundance
sigma_p <- 0.6  # process noise standard deviation
r <- 0.8        # Ricker productivity parameter
K <- 50         # Carrying capacity
# Mean-bias corrected process noise:
proc_noise <- rnorm(N, -(sigma_p^2)/2, sigma_p)

@@

```{r, results="hide"}
stan_model_missing <-
'data {
  int<lower=0> N; // rows of data
  vector[N] y; // log(numbers) at time t
  real<lower=0> K_upper; // upper boundary on K
  int<lower=0> Nmissing; // number of missing values
  int missing_id[Nmissing]; // IDs of missing values
}
parameters {
  real<lower=0, upper=K_upper> K;
  real r;
  real<lower=0> sigma_proc;
  real y_missing[Nmissing]; // imputed missing values
}
transformed parameters {
  vector[N] y_impute; // y with some imputed
  for (i in 1:N) {
    y_impute[i] <- y[i];
  }
  for (i in 1:Nmissing) {
    y_impute[missing_id[i]] <- y_missing[i];
  }
}
model {
  sigma_proc ~ cauchy(0, 5);
  r ~ cauchy(0, 5);
  for (i in 2:N) {
   y_impute[i] ~
     normal(y_impute[i-1] + r * (1 - exp(y_impute[i-1]) / K),
            sigma_proc);
  }
}
'
stan_ricker_missing <- stan_model(model_code = stan_model_missing)
```

```{r, results="hide"}
missing_id <- sample(seq_len(N), 4)
y_missing <- y
y_missing[missing_id] <- 9999 # Stan can't handle NAs; give it fake data
m_missing <- sampling(
  stan_ricker_missing,
  data = list(N = N, y = log(y_missing), 
    K_upper = max(y_missing[-missing_id]) * 2, 
    Nmissing = length(missing_id), missing_id = missing_id),
  iter = 4000,
  pars = c("K", "r", "sigma_proc", "y_impute"))
```

@@

pch <- rep(20, N)
col <- rep("black", N)
pch[missing_id] <- 21
col[missing_id] <- "blue"
plot(x, y, type = "o", pch = pch, ylim = c(0, max(y_missing[-missing_id]) * 1.1), col = col)
imputed <- exp(apply(p$y_impute, 2, median))
imputed_l <- exp(apply(p$y_impute, 2, quantile, prob = 0.1))
imputed_u <- exp(apply(p$y_impute, 2, quantile, prob = 0.9))
imputed_ll <- exp(apply(p$y_impute, 2, quantile, prob = 0.25))
imputed_uu <- exp(apply(p$y_impute, 2, quantile, prob = 0.75))
points(x[missing_id], imputed[missing_id], col = "red", pch = 21, cex = 1.5)
segments(x[missing_id], imputed_l[missing_id], 
  x[missing_id], imputed_u[missing_id], col = "red", lwd = 1)
segments(x[missing_id], imputed_ll[missing_id], 
  x[missing_id], imputed_uu[missing_id], col = "red", lwd = 2.5)
```

>>>>

```{r stan-impute1}
set.seed(1)
N <- 50         # number of time steps
x <- 1:N        # time step values
y <- rep(NA, N) # vector to hold (scaled) abundance values
y[1] <- 1       # initial scaled abundance
sigma_p <- 0.3  # process noise standard deviation
r <- 0.8        # Ricker productivity parameter
K <- 50         # Carrying capacity
# Mean-bias corrected process noise:
proc_noise <- rnorm(N, -(sigma_p^2)/2, sigma_p)

@@

```{r, results="hide"}
stan_model_missing <-
'data {
  int<lower=0> N; // rows of data
  vector[N] y; // log(numbers) at time t
  real<lower=0> K_upper; // upper boundary on K
  int<lower=0> Nmissing; // number of missing values
  int missing_id[Nmissing]; // IDs of missing values
}
parameters {
  real<lower=0, upper=K_upper> K;
  real r;
  real<lower=0> sigma_proc;
  real y_missing[Nmissing]; // imputed missing values
}
transformed parameters {
  vector[N] y_impute; // y with some imputed
  for (i in 1:N) {
    y_impute[i] <- y[i];
  }
  for (i in 1:Nmissing) {
    y_impute[missing_id[i]] <- y_missing[i];
  }
}
model {
  sigma_proc ~ cauchy(0, 5);
  r ~ cauchy(0, 5);
  for (i in 2:N) {
   y_impute[i] ~
     normal(y_impute[i-1] + r * (1 - exp(y_impute[i-1]) / K),
            sigma_proc);
  }
}
'
stan_ricker_missing <- stan_model(model_code = stan_model_missing)

stan_model_missing1 <-
'data {
  int<lower=0> N; // rows of data
  vector[N] y; // log(numbers) at time t
  real<lower=0> K_upper; // upper boundary on K
  int<lower=1> missing_id; // ID of missing values
}
parameters {
  real<lower=0, upper=K_upper> K;
  real r;
  real<lower=0> sigma_proc;
  real y_missing; // imputed missing values
}
transformed parameters {
  vector[N] y_impute; // y with some imputed
  for (i in 1:N) {
    y_impute[i] <- y[i];
  }
  y_impute[missing_id] <- y_missing;
}
model {
  sigma_proc ~ cauchy(0, 5);
  r ~ cauchy(0, 5);
  for (i in 2:N) {
   y_impute[i] ~
     normal(y_impute[i-1] + r * (1 - exp(y_impute[i-1]) / K),
            sigma_proc);
  }
}
'
stan_ricker_missing1 <- stan_model(model_code = stan_model_missing1)

```

```{r, results="hide"}
missing_id <- sample(seq_len(N), 1)
y_missing <- y
y_missing[missing_id] <- 9999 # Stan can't handle NAs; give it fake data
m_missing <- sampling(
  stan_ricker_missing1,
  data = list(N = N, y = log(y_missing), 
    K_upper = max(y_missing[-missing_id]) * 2, 
    # Nmissing = length(missing_id), 
    missing_id = missing_id),
  iter = 2000,
  pars = c("K", "r", "sigma_proc", "y_impute"))
```

@@

pch <- rep(20, N)
col <- rep("black", N)
pch[missing_id] <- 21
col[missing_id] <- "blue"
plot(x, y, type = "o", pch = pch, ylim = c(min(y_missing), max(y_missing[-missing_id]) * 1.1), col = col, log = "y")
imputed <- exp(apply(p$y_impute, 2, median))
imputed_l <- exp(apply(p$y_impute, 2, quantile, prob = 0.1))
imputed_u <- exp(apply(p$y_impute, 2, quantile, prob = 0.9))
imputed_ll <- exp(apply(p$y_impute, 2, quantile, prob = 0.25))
imputed_uu <- exp(apply(p$y_impute, 2, quantile, prob = 0.75))
points(x[missing_id], imputed[missing_id], col = "red", pch = 21, cex = 1.5)
segments(x[missing_id], imputed_l[missing_id], 
  x[missing_id], imputed_u[missing_id], col = "red", lwd = 1)
segments(x[missing_id], imputed_ll[missing_id], 
  x[missing_id], imputed_uu[missing_id], col = "red", lwd = 2.5)
```

### 2015-11-25 cv-body.tex
Quick update to CV

@@

\section{Manuscripts in review}\label{manuscripts-in-review}

\begin{description}
\itemsep3pt\parskip0pt\parsep0pt
\item[2015]
Monnahan, C.C., K. Ono, S.C Anderson, M.B. Rudd, A.C. Hicks, F.
Hurtado-Ferro, K.F. Johnson, P.T. Kuriyama, R.R. Licandeo, C.C. Stawitz,
I.G. Taylor, J.L. Valero. The effect of length bin structures on growth
estimation in integrated age-structured stock assessments. Submitted.
\item[2015]
Kuriyamaa, P.T., F. Hurtado-Ferro, K. Ono, A.C. Hicks, I.G. Taylor, R.R.
Licandeo, K.F. Johnson, S.C. Anderson, C.C. Monnahan, M.B. Rudd, C.C.
Stawitz, J.L. Valero. An empirical weight-at-age approach reduces
estimation bias compared to modeling parametric growth in integrated,
statistical stock assessment models when growth is time varying.
Submitted.
\item[2015]
Trebilco, R., N.K. Dulvy, \textbf{S.C. Anderson}, A.K. Salomon. The
paradox of inverted biomass pyramids in kelp forest fish communities. In
revision.
\end{description}

>>>>

Monnahan, C.C., K. Ono, S.C Anderson, M.B. Rudd, A.C. Hicks, F.
Hurtado-Ferro, K.F. Johnson, P.T. Kuriyama, R.R. Licandeo, C.C. Stawitz,
I.G. Taylor, J.L. Valero. The effect of length bin width on growth
estimation in integrated age-structured stock assessments. In press.
\url{http://doi.org/10.1016/j.fishres.2015.09.007}
Kuriyamaa, P.T., F. Hurtado-Ferro, K. Ono, A.C. Hicks, I.G. Taylor, R.R.
Licandeo, K.F. Johnson, S.C. Anderson, C.C. Monnahan, M.B. Rudd, C.C.
Stawitz, J.L. Valero. An empirical weight-at-age approach reduces
estimation bias compared to modeling parametric growth in integrated,
statistical stock assessment models when growth is time varying. In
press. \url{http://doi.org/10.1016/j.fishres.2015.11.002}

@@
